Comparison of FDR methods on 16S microbiome data with SummarizedBenchmark

### 2018-02-20 datasets/microbiome/microbiome-schubert.Rmd
Verify microbiome schubert knits

# Keep only samples with both metadata and 16S data
keep_samples <- intersect(colnames(otu), meta$sample_id)
otu <- otu[, keep_samples]
meta <- filter(meta, 'sample_id' %in% keep_samples)
```

@@

## Update metadata with new samples
meta <- filter(meta, sample_id %in% colnames(otu))

@@

```{r, schubert-addphylo, eval=TRUE}
res <- dplyr::separate(res, otu, 
                       c("kingdom", "phylum", "class", "order",
                         "family", "genus", "species", "denovo"), 
                       sep = ";", remove = FALSE)
```

>>>>

# Keep only samples with both metadata and 16S data
keep_samples <- intersect(colnames(otu), meta$sample_id)
otu <- otu[, keep_samples]
meta <- filter(meta, sample_id %in% keep_samples)
```

@@

## Update metadata with new samples
meta <- dplyr::filter(meta, sample_id %in% colnames(otu))

@@

```{r, schubert-addphylo, eval=TRUE}
res <- tidyr::separate(res, otu, 
                       c("kingdom", "phylum", "class", "order",
                         "family", "genus", "species", "denovo"), 
                       sep = ";", remove = FALSE)
```
